On the properties of discs around accreting brown dwarfs

### 2010-07-16 BDD_submit/paper.tex
Some minor typos and added Herschel filters
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2385 25464f21-6099-402c-b30a-640f1d40d38b

The magnitudes and colours presented in this paper are available both
as individual magnitudes and as isochrones or mass tracks. Photometric
magnitudes have also been derived for several other systems and are
available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$ and $B_t$
\citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
\citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
\citep{fukugita_1996}, 2MASS $JHK_s$
\citep{cohen_2003,skrutskie_2006}, MKO \textit{JHK}
\citep{simons_2002,tokunaga_2002}, UKIRT \textit{ZYJHK}
\citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
\citep{neugebauer_1984} and SCUBA \textit{450WB} and \textit{850WB}
\citep{holland_1999}. For further information on these magnitudes,
such as the filter responses used and the adopted zeropoints please
refer to the website.

\textit{Monochromatic fluxes}

@@

We also directly compared the magnitudes and colours of our naked BD
systems with the lowest accretion rate (-12
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ to those published in
\cite{chabrier_2000}, in the same photometric system
(\textit{CIT}). We found significant colour differences ($\delta
(J-K)\le$ 0.1), between our derived values and those of
\cite{chabrier_2000}. As a further check we derived the
magnitudes in the \cite{bessell_1998} system (by both adopting
the published zero points, and by using a Vega reference spectrum),
and applied conversions of \cite{leggett_1992}\footnote{We have
  also included the wavelength shift mentioned in
  \cite{stephens_2004}}, to the \textit{CIT} system. For each
method we failed to match the magnitudes and colours published in
\cite{chabrier_2000}. As a final test we passed the downloaded,
unaltered, atmospheric spectra directly through the filter response
program, without interpolation, for the closest matches in log(g) and
$T_{\rm eff}$ from the interior models published in
\cite{chabrier_2000}. These magnitudes and colours also failed
to match. Therefore, we must conclude that the most likely cause of
the mismatch is due to improvements in the model atmospheres available
online\footnote{http://perso.ens-lyon.fr/france.allard/} (this is
likely as the models available online, have a later time stamp,
$\approx$\,2005 compared to 2000). For the final published magnitudes,
for the naked systems, we have used a similar wavelength resolution as
in our BDD systems, i.e. 200 logarithmically spaced points. This means
that magnitudes derived from these spectra will differ slightly from
those derived from the full spectra, but this effect is negligible,
and increased resolution for only some of our model grid (i.e naked
stars) will hamper comparison between the models.

>>>>

The magnitudes and colours presented in this paper are available both
as individual magnitudes and as isochrones or mass tracks. Photometric
magnitudes have also been derived for several other systems and are
available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$ and $B_t$
\citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
\citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
\citep{fukugita_1996}, 2MASS $JHK_s$
\citep{cohen_2003,skrutskie_2006}, MKO \textit{JHK}
\citep{simons_2002,tokunaga_2002}, UKIRT \textit{ZYJHK}
\citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
\citep{neugebauer_1984}, SCUBA 450WB and 850WB
\citep{holland_1999} \footnote{The SCUBA 2 filter responses are similar
  to SCUBA}, Herschel PACS blue, green and red \citep{poglitsch_2008,
  poglitsch_2010} and Herschel SPIRE, 250, 350 and 500
\citep{griffin_2008,griffin_2010}. For further information on these
magnitudes, such as the filter responses used and the adopted
zeropoints please refer to the website.

@@

We also directly compared the magnitudes and colours of our naked BD
systems with the lowest accretion rate (\logmdot -12) to those
published in \cite{chabrier_2000}, in the same photometric system
(\textit{CIT}). We found significant colour differences ($\delta
(J-K)\le$ 0.1), between our derived values and those of
\cite{chabrier_2000}. As a further check we derived the magnitudes in
the \cite{bessell_1998} system (by both adopting the published zero
points, and by using a Vega reference spectrum), and applied
conversions of \cite{leggett_1992}\footnote{We have also included the
  wavelength shift mentioned in \cite{stephens_2004}}, to the
\textit{CIT} system. For each method we failed to match the magnitudes
and colours published in \cite{chabrier_2000}. As a final test we
passed the downloaded, unaltered, atmospheric spectra directly through
the filter response program, without interpolation, for the closest
matches in log(g) and $T_{\rm eff}$ from the interior models published
in \cite{chabrier_2000}. These magnitudes and colours also failed to
match. Therefore, we must conclude that the most likely cause of the
mismatch is due to improvements in the model atmospheres available
online\footnote{http://perso.ens-lyon.fr/france.allard/} (this is
likely as the models available online, have a later time stamp,
$\approx$\,2005 compared to 2000). For the final published magnitudes,
for the naked systems, we have used a similar wavelength resolution as
in our BDD systems, i.e. 200 logarithmically spaced points. This means
that magnitudes derived from these spectra will differ slightly from
those derived from the full spectra, but this effect is negligible,
and increased resolution for only some of our model grid (i.e naked
stars) will hamper comparison between the models.
